%!TEX root=../../main.tex

Now we analyze the structure of \( \calGl \) with the goal of establishing a
fully convex reformulation for deep ReLU networks.
This recursive constraint set encodes several key features of ReLU networks:
(i) weight sharing, through \( \Wll \), (ii) low-rank neurons, through the
outer-products \( \Tl_{j_1, \ldots, j_{l-1}, i_l} \otimes \Wll_{j_l} \),
(iii) the layer width, through
\( \sum_{j_l=1}^{p_l} \abs{\calI_{j_l}^{(l)}} \leq d_l \),
and (iv) activation cone membership.
Out of these constraints, (i) to (iii) are affected by the width of the
network.
We will show that these constraints vanish for sufficiently wide models.

Let \( \phi_l : \cbr{1, -1} \times [p_l] \times [d_{l+1}] \rightarrow [2 p_l \cdot d_{l+1}] \)
be a one-to-one function from the index triplets
\( (s, j_l, i_{l+1}) \) to a unique index in \( [2 p_l \cdot d_{l+1}] \).
Using this notation, consider the tensor constraint defined recursively by
\( \calC^{(1)} = \R^{d_0 \times d_1} \) and
\begin{equation}\label{eq:recursive-cone-constraint}
    \begin{aligned}
        \calC^{(l+1)}
         & = \bigg\{
        \Tll \in \R^{d_0 \times p_1 \cdots \times p_{l} \times d_{l+1}}
        :
        \Tll_{j_{l}, i_{l+1}}
        = \Tl_{ \phi_l(1, j_l, i_{l+1})}
        - \Tl_{ \phi_l(-1, j_l, i_{l+1})},
        \text{ where}   \\
         & \hspace{3em}
        \Tl_{\phi_l(1, j_l, i_{l+1})}, \Tl_{ \phi_l(-1, j_l, i_{l+1})}
        \in \calK^{(l)}_{j_{l}}, \text{ and }
        \Tl \in \calC^{(l)}
        \bigg\}
    \end{aligned}
\end{equation}
The construction of \( \calCl \) requires the dimension of the
last order, \( d_{l} \), to satisfy \( d_{l} \geq 2 p_{l} d_{l+1} \);
otherwise, we could not embed \( \Tll \) into \( \Tl \).
It is straightforward to show that \( \calC^{(l)} \) is a convex cone
(\cref{lemma:convex-recursive-cone-constraint}).
More importantly, \( \calC^{(l)} \) is exactly the constraint set obtained
by making the network wide enough that the weight sharing, low-rank,
and width constraints in \( \calGl \) vanish.

\begin{restatable}[Constraint Convexification]{proposition}{constraintConvexification}%
    \label{prop:constraint-convexification}
    If \( d_l \geq 2 p_l d_{l+1} \) for every \( l \in [L-1]  \), then
    \( \calG^{(L)} = \calC^{(L)} \).
\end{restatable}

Although short, \cref{prop:constraint-convexification} is the critical
result for our convex reformulation.
It says that if the network is sufficiently wide, \( \calGk \) is convex and
Problem~\ref{eq:non-convex-tensor-program} is a fully convex optimization
problem.
Recalling that the \( d_L = c \), the condition \( d_l \geq 2 p_l d_{l+1} \)
is equivalent to \( d_l \geq c \, 2^{L-l} \prod_{i = l+1}^{L} p_l \).
In other words, the network must be shaped like a pyramid, where each
layer is multiplicatively larger than the succeeding one,
for the constraint set to convexify and \( \calGk = \calCk \) to hold.
This yields the following corollary.
\begin{corollary}\label{cor:convex-tensor-program}
    If \( d_l \geq c \, 2^{L-l} \prod_{i = l}^{L-1} p_l \) for every
    \( l \in [L-1]  \), then
    \begin{equation*}
        \min_{\theta = (W^{(1)}, \ldots, \Wk)} \calL\rbr{f_{\theta}(X), y},
    \end{equation*}
    is equivalent to the convex tensor program
    \begin{equation}\label{eq:convex-tensor-program}
        \min_{\Tk}
        \calL\rbr{\Xk \odot \Tk, y} \quad \text{s.t.} \quad
        \Tk \in \calC^{(k)}.
    \end{equation}
\end{corollary}

Next we show that the solution mapping for Problem~\ref{eq:convex-tensor-program}
relies on the recursive decomposition specified by membership in \( C^{(k)} \).
Moreover, the number of neurons in each layer corresponds to the number of
non-zero activation patterns.

\begin{restatable}[Solution Mapping]{lemma}{tensorSolutionMapping}%
    \label{lemma:convex-tensor-solution-mapping}
    Assume \( d_l \geq 2 p_l d_{l+1} \) for all \( l < k \).
    Fix \( \Tk \in \calCk \) and for \( 1 < l < k \), let \( \Tl \in \calCl \)
    be the associated recursive factor.
    Define the set of non-zero neurons as
    \[
        \calA(\Tl) = \cbr{i_{l} \in [d_l] : \Tl_{i_{l}} \neq 0}.
    \]
    For every \(s \in \cbr{1, -1} \), \( j_l \in [p_l] \), and
    \( i_{l+1} \in [d_{l+1}] \), the associated rows of \( W^{(l+1)} \) are
    \[
        W^{(l+1)}_{\phi_l(s, j_l, i_{l+1})}
        = e_{i_{l+1}} \rbr{s \cdot \mathds{1}\rbr{\phi_l(s, j_l, i_{l+1}) \in \calA(\Tl)}},
    \]
    where \( e_{i_{l+1}} \in \R^{d_{l+1}} \) is the \( i_{l+1}^{\text{th}} \)
    basis vector.
    Finally, let \( W^{(1)} = T^{(1)} \)
    so that the network parameters are
    \( \theta = \rbr{W^{(1)}, \ldots, W^{(k)}} \).
    Then \( X^{(k)} \odot T^{(k)} = f_\theta(X) \).
\end{restatable}

Given any tensor model \( \Tk \in \calCk \), \cref{lemma:convex-tensor-solution-mapping}
provides a simple way of computing an equivalent neural network \( f_\theta \).
Moreover, it shows that the number of non-zero neurons in the
\( l^{\text{th}} \) layer of the network is given by
\( m_{l}(\Tk) = \abs{\calA(\Tl)} \).
Collecting these widths as \( \Delta(\Tk) = \rbr{m_1(\Tk), \ldots, m_{L-1}(\Tk)} \),
the optimal solutions to Problem~\ref{eq:convex-tensor-program} define
a Pareto frontier of minimal-width networks with the same optimal
value as the convex reformulation.
Let
\begin{equation}\label{eq:tensor-optima}
    \calO^* = \argmin_{\Tk \in \calCk} \calL(\Xk \odot \Tk, y)
\end{equation}
be the set of optimal solutions to Problem~\ref{eq:convex-tensor-program}.
Then the frontier of minimal widths is given as follows:
\begin{equation}
    \calD^* :=
    \cbr{\Delta(\Tkopt)
        : \Tkopt \in \calO^* \text{ s.t. } \nexists T^{(L)'} \in \calO^*,
        \Delta(T^{(L)'}) \prec \Delta(\Tkopt)}.
\end{equation}

We now exhibit a solution \( \Tkopt \in \calO^* \) which allows us to
upper bound \( m^*_l \) for at least one point
\( \Delta^* = (m^*_1, \ldots, m^*_{L-1}) \in \calD^* \).

\begin{restatable}{proposition}{minimumSolutionWidth}\label{prop:convex-minimal-solution-width}
    There exists at least one solution to the convex tensor optimization
    program in \cref{eq:convex-tensor-program} satisfying
    \( m_l(\Tk) \leq c \, n^{L - l} \) for every
    \( l \in \cbr{1, \ldots, L-1} \).
\end{restatable}

As an immediate result, we obtain the main theorem of this section.

\begin{restatable}{theorem}{deepConvexReformulation}\label{thm:deep-convex-reformulation}
    If for every \( l \in [L-1]  \) it holds that
    \( d_l \geq m^{*}_{l} \) for some threshold \( m^{*}_{l} \leq c \, n^{L - l} \),
    then the deep ReLU network training problem
    \begin{equation*}
        \min_{\theta = (W^{(1)}, \ldots, \Wk)} \calL\rbr{f_{\theta}(X), y},
    \end{equation*}
    is equivalent to the convex tensor program
    \begin{equation}
        \min_{\Tk}
        \calL\rbr{\Xk \odot \Tk, y} \quad \text{s.t.} \quad
        \Tk \in \calC^{(k)}.
    \end{equation}
\end{restatable}

In comparison to \cref{cor:convex-tensor-program}, this theorem reduces
the width requirement on the \( l^{\text{th}} \) layer of the neural network
from \( d_l \geq c \, 2^{(L- l)} \prod_{i=l}^{L-1} p_l \) to
\( d_l \geq m^*_{l} \) where \( m^*_{l} \) is a data-dependent threshold
bounded as \( m^*_{l} \leq c \, n^{L - 1} \).
If the number of layers in the network, \( L \), is fixed ahead of time, then
this is fully polynomial in the input data.
Moreover, the bound on \( m^*_l \) is tight with existing results on
convex reformulations.
For example, \citep{sahiner2021vector} show that a convex reformulation exists
for two-layer ReLU networks with vector outputs if \( d_1 \geq m_1^* \) for
\( m_1^* \leq c \, n \).
Specializing \cref{thm:deep-convex-reformulation} to \( L = 2 \) yields exactly
the same condition.

\subsection{Deep Gated ReLU Networks}\label{sec:deep-gated-relu}

In \cref{chapter:fast-optimization}, we showed that two-layer neural networks
with Gated ReLU activations admit a simple, unconstrained convex
reformulation.
Given a fixed dataset \( (X, y) \), we also showed that gated ReLU networks
form the same hypothesis space as two-layer ReLU networks --- that is, as long
as no singular activation patterns are included in the Gated ReLU network.
This allowed us to develop fast, unconstrained optimization methods
which either exactly solve (in the unregularized setting) or approximate
(in the regularized setting) the two-layer ReLU problem.
Now we consider deep gated ReLU networks and develop an equivalent theory.

Recall that the gated ReLU activation function is given by
\[
    \phi_{G^{(l)}}\rbr{Z^{(l)}, W^{(l)}}
    = \mathds{1}\rbr{Z^{(l)} G^{(l)} \geq 0} \circ (Z^{(l)} W^{(l)}),
\]
where \( G^{(l)} \in \R^{d_{(l-1)} \times d_{l}} \) is a matrix of the gate
vectors, the indicator function is taken element-wise over
\( Z^{(l)} G^{(l)} \), and \( \circ \) indicates the element-wise product.
A deep gated ReLU network is then defined by
\begin{equation}\label{eq:deep-gated-relu}
    g_\theta(X) = \Zk \Wk,
    \quad \text{where} \quad
    \Zll = \phi_{G^{(l)}}\rbr{\Zl, W^{(l)}}.
\end{equation}
While the activations patterns generated by in the first-layer of a gated
ReLU network are necessarily the same as those generated by a ReLU network, the
space of attainable features \( Z^{(2)} \) is not equivalent unless all
singular activation patterns are omitted (\cref{thm:cone-elimination}).
However, we can handle this issue by defining a maximal set of achievable
patterns as in the ReLU setting.

Given any architecture \( \Delta \), define the set of activation patterns
by a conformal Gated ReLU network with that architecture to be
\begin{equation}\label{eq:gatd-relu-l-activation-patterns}
    \begin{aligned}
        \calDl_{\text{gated}}(\Delta) = \big\{
        \Dl_{j_l} =
        \diag\rbr{\mathds{1}\rbr{g_{\theta_{l-1}}(X) u \geq 0}}
        : \theta^{(l-1)} \in \Theta_\Delta^{(l-1)}, u \in \R^{d_{l}}
        \big\},
    \end{aligned}
\end{equation}
where we write \( \Theta^{(l-1)}_{\Delta} \) for the parameter space
of the sub-network with architecture \( \Delta \).
Similar to \cref{lemma:activation-patterns}, a canonical set of
patterns is obtained taking all the layers to be sufficiently wide.
\begin{restatable}{lemma}{gatedLimitingActivationSet}\label{lemma:gated-activation-patterns}
    The set of gated ReLU activation patterns in the \( l^{\text{th}} \) layer has a
    finite limit, call it \( \calDl_{\text{gated}} \), obtained by taking the hidden layer
    width \( d_{k} \rightarrow \infty \) for each \( k \in [l] \).
    \begin{equation}\label{eq:gated-limiting-activation-set}
        \calDl_{\text{gated}} = \lim_{\Delta \rightarrow \infty} \calDl_{\text{gated}}(\Delta).
    \end{equation}
\end{restatable}
We write \( p_{l}^{\text{gated}} = \abs{\calDl} \) for the number of unique activation
patterns in the \( l^{\text{th}} \) layer.

Equipped with the set of gated ReLU activation patterns, we
now define an explicit version of gated ReLU networks.
For \( L = 1 \), the explicit gated ReLU network is provided by
\cref{chapter:fast-optimization} and is just
\begin{equation}\label{eq:explicit-gated-relu}
    g^{\text{exp}}_{\theta_{1}}(X)
    = \begin{bmatrix}
        D^{(1)}_{1} X W^{(1)}_{\cdot, 1} \cdots
        D^{(1)}_{p_1} X W^{(1)}_{\cdot, p_1}
    \end{bmatrix}
    = \mathbf{D}^{(1)}_{\text{gated}} \circ X W^{(1)},
\end{equation}
where \( D^{(1)}_{j_1} \in \calD^{(1)} \) and
\( \mathbf{D}^{(1)}_{\text{gated}}\) is the matrix whose \( i_1^{\text{th}} \)
column is given by the diagonal of \( D^{(1)}_{i_1} \).
Since \( \calD^{(1)} \) has no dependence on the network structure, this
captures the first-layer feature map of any two-layer Gated ReLU network.
The following definition uses this base case to define the explicit gated ReLU
network for \( l > 1 \).
\begin{definition}\label{def:explicit-gated-relu}
    An explicit gated ReLU network is defined recursively by
    \begin{equation}
        g^{\text{exp}}_{\theta_{l}}(X)
        = \begin{bmatrix}
            D^{(l)}_{1} g^{\text{exp}}_{\theta_{l-1}}(X) W^{(l)}_{\cdot, 1}  \cdots
            D^{(l)}_{p_l^{\text{gated}}} g^{\text{exp}}_{\theta_{l-1}}(X) W^{(l)}_{\cdot, p_l^{\text{gated}}}
        \end{bmatrix}
        = \mathbf{D}_{\text{gated}}^{(l)} \circ g^{\text{exp}}_{\theta_{l-1}}(X) W^{(l)},
    \end{equation}
    such that \( g_{\theta_0}^{\text{exp}}(X) = X \), and
    \( g_{\theta_L}^{\text{exp}}(X) = g^{\text{exp}}_{\theta_{L-1}}(X) W^{(L)} \).
\end{definition}

Explicit gated ReLU networks eliminate the dependence on gate
matrices \( G^{(l)} \) by assigning one neuron per activation pattern.
Note, however, that this does not produce an equivalent model space to standard
gated ReLU networks.
This is because the feature map \( g^{\text{exp}}_{\theta_{l}}(X) \) associated
with a specific \( \theta \) may not be generate some patterns which are active
in layer \( (l+1) \) of that same model.
Additionally, \( g^{\text{exp}} \) has only one neuron per pattern,
whereas a proper gated ReLU network may have multiple neurons with the same
pattern depending on the choice of gate vectors.
Explicit gated ReLU and gated ReLU networks are guaranteed to be equivalent
when \( L = 2 \) and \( c = 1 \), in which case we reduce to the setting
of \cref{chapter:fast-optimization}.

Unrolling the definition of \( g_\theta^{\text{exp}} \),
we observe that
\[
    g_\theta^{\text{exp}}(X) =
    \sum_{j_1 = 1}^{p^{\text{gated}}_1} \cdots \sum_{j_{L-1} = 1}^{p^{\text{gated}}_{L-1}}
    D^{(1)}_{j_1} \cdots D^{(L-1)}_{j_{L-1}} X
    W^{(1)}_{\cdot, j_1} \rbr{W^{(2)}_{j_1, j_2} \cdots W^{(2)}_{j_{L-2}, j_{L-1}}} W^{(L)}_{j_{L-1}}.
\]
The product of network weights in this sum can be interpreted as the
decomposition of an \( L+1 \)-order tensor, which we define as follows:
\begin{equation}\label{eq:gated-relu-tensor}
    \tilde{T}^{(L)}_{j_1, \ldots, j_{L-1}}
    = W^{(1)}_{\cdot, j_1} \otimes W^{(L)}_{j_{L-1}} \rbr{W^{(2)}_{j_1, j_2}
    \cdots W^{(2)}_{j_{L-2}, j_{L-1}}} .
\end{equation}
Crucially, \( \tilde{T}^{(L)} \) satisfies
\( g_\theta^{\text{exp}}(X) = \tXk \odot \tilde{T}^{(L)} \),
where \( \tXk \) is defined with respect to the gated ReLU
activations.
We also note that the slice \( \tilde{T}^{(L)}_{j_1, \ldots, j_{L-1}} \) is
rank-one.
This provides the underlying intuition for the following layer elimination
lemma.

\begin{restatable}[Gated ReLU Layer Elimination]{proposition}{gatedReLULayerElimination}%
    \label{prop:gated-layer-elimination}
    Let \( \calH^{(0)} = \R^{d_0 \times d_1} \) and define
    \begin{equation}\label{eq:gated-tensor-decomp}
        \begin{aligned}
            \calHll
             & := \bigg\{ \Tll
            \in \R^{d_{0} \times p_{1}^{\text{gated}} \times \cdots \times p_{l}^{\text{gated}} \times d_{l+1}}
            :  \exists \, \Tl \in \calHl
            \text{ and } W^{(l+1)} \in \R^{p_l^{\text{gated}} \times p^{\text{gated}}_{l+1}} \\
             & \hspace{2em} \text{ such that } \Tll_{j_1, \ldots, j_{l}}
            = \Tl_{j_1, \ldots, j_{l}}
            \otimes W^{(l+1)}_{j_l}
            \bigg\}.
        \end{aligned}
    \end{equation}
    There exists \( \Tl \in \calHl \) such that
    the explicit gated ReLU model at layer \( l+2 \) satisfies
    \begin{equation}\label{eq:gated-layer-to-tensorize}
        Z^{(l+2)} = \mathbf{D}^{(l+1)}_\text{gated} \circ
        \sbr{\sum_{j_l=1}^{p_l^{\text{gated}}} \rbr{\Dl_{j_l} \sbr{\tXl \odot \Tl_{j_l}}}
        \otimes W^{(l+1)}_{j_l}}
    \end{equation}
    if and only if there exists \( \Tll \in \calGll \) satisfying
    \[
        Z^{(l+2)} =
        \mathbf{D}^{(l+1)}_\text{gated} \circ \sbr{\tXll \odot \Tll}.
    \]
\end{restatable}

As a corollary, we demonstrate that the explicit gated ReLU problem
is equivalent to a tensor program with non-convex constraints.

\begin{restatable}{corollary}{nonConvexGatedReLU}\label{cor:non-convex-gated-relu}
    The training problem for the explicit gated ReLU network,
    \begin{equation}\label{eq:explicit-gated-program}
        \min_{\theta = (W^{(1)}, \ldots, \Wk)} \calL\rbr{g^{\text{exp}}_{\theta}(X), y},
    \end{equation}
    is equivalent to the following tensor program with non-convex
    constraints:
    \begin{equation}\label{eq:non-convex-gated-relu-program}
        \min_{\Tk \in \calHk} \calL\rbr{\tXk \odot \Tk, y}.
    \end{equation}
\end{restatable}

This proposition is exactly the gated ReLU equivalent of
\cref{cor:non-convex-tensor-program} given in
\cref{sec:tensor-representation}, although with several
important differences.
Firstly, since \( g^{\text{exp}}_\theta \) is an explicit gated ReLU network,
the activation cones \( \calK^{(l)}_{j_l} \) do not appear in the recursive
constraint (compare to \( \calGl \) in \cref{eq:rank-tensor-decomp}).
Similarly, since the activations in the explicit gated ReLU problem are fixed,
each tensor slice \( \Tl_{j_1, \ldots, j_l} \) is restricted to be rank-one.
This latter constraint can be alleviated by including
multiples of each activation pattern in the non-convex network.

Let \( g^{\text{dup}}_{\theta} \) be an duplicated version of the explicit
gated ReLU network which, in the \( l^{\text{th}} \) layer, contains
\( d_{l+1} \) copies of each activation pattern.
That is to say, let \( d^{(l)}_{j_l} = \diag\rbr{D^{(l)}_{j_l}} \)
and set
\[
    \mathbf{D}^{(l)}_{\text{dup}} =
    \begin{bmatrix}
        [\underbrace{d^{(l)}_{1} \cdots d^{(l)}_{1}}_{d_{l+1}}] \cdots
        [\underbrace{d^{(l)}_{p_l^{\text{gated}}} \cdots d^{(l)}_{p_l^{\text{gated}}}}_{d_{l+1}}]
    \end{bmatrix},
\]
so that \( l^{\text{th}} \) layer has \( d_l = p_l d_{l+1} \) activation
patterns.
Unrolling this recursion, we have \( d_l = c \prod_{k = l}^{L-1} p_l \).
Now we can define \( g_{\theta_0}^{\text{dup}}(X) = X \),
\( g^{\text{dup}}_{\theta_{l}}(X)
= \mathbf{D}_{\text{dup}}^{(l)} \circ g^{\text{dup}}_{\theta_{l-1}}(X) W^{(l)}, \)
and \( g_{\theta_L}^{\text{dup}}(X) = g^{\text{dup}}_{\theta_{L-1}}(X) W^{(L)} \).
This leads to our convex reformulation.
\begin{restatable}{theorem}{convexGatedReLU}\label{thm:convex-gated-relu}
    The training problem for the duplicated gated ReLU network,
    \begin{equation}\label{eq:duplicated-gated-relu-program}
        \min_{\theta = (W^{(1)}, \ldots, \Wk)} \calL\rbr{g^{\text{dup}}_{\theta}(X), y},
    \end{equation}
    is equivalent to the following unconstrained tensor program:
    \begin{equation}\label{eq:convex-gated-relu-program}
        \min_{\Tk} \calL\rbr{\tXk \odot \Tk, y}.
    \end{equation}
\end{restatable}
Just as in the two-layer case, switching to gated ReLU activations decouples
activation patterns from the neuron weights, leading to a fully unconstrained
problem.
Indeed, Problem~\ref{eq:convex-gated-relu-program} is
identical to the convex reformulation from the previous section
(Problem~\ref{eq:convex-tensor-program}) except that the recursive cone
constraints specified by \( \calCk \) have vanished.
However, unlike for Problem~\ref{eq:convex-tensor-program}, we cannot
avoid including \( d_{l+1} \) duplicated activation patterns in the non-convex
model (i.e.\ the duplicated Gated ReLU network).
Indeed, the last result in this section shows that these additional
patterns are necessary to represent the full space of Gated ReLU models.

\begin{restatable}{proposition}{duplicatedEquivalence}%
    \label{prop:duplicated-equivalence}
    Every gated ReLU model \( g_\theta \) can be represented as a duplicated
    Gated ReLU model, \( g_\theta^{\text{dup}} \), but not every
    duplicated gated ReLU model is a gated ReLU model.
\end{restatable}

Duplicated Gated ReLU models are strictly more expressive than gated ReLU
models because the intermediate feature maps \( g^{\text{dup}}_{\theta_{l}} \)
may not generate all of the activation patterns used in the succeeding layers.

\subsection{Deep Cone Decompositions}\label{sec:deep-cone-decompositions}

We conclude by extending the equivalence of two-layer ReLU and Gated ReLU networks
shown in \cref{sec:relu-grelu-equivalence} to deep networks.
Recall that we call an activation pattern \( \Dl_{j_l} \in \calDl \)
\emph{singular} if the cone \( \calKl_{j_l} \)  is contained in a strict
subspace of \( \R^{d_0 \times p_1 \times \cdots \times p_{l-1}} \),
implying that
\( \calKl_{j_l} - \calKl_{j_l} \subset \R^{d_0 \times p_1 \times \cdots \times p_{l-1}} \).
We use the set \( \calDl_{\text{ns}} \subseteq \calDl \) to denote the subset
of ReLU activation patterns in the \( l^{\text{th}} \) layer which are
non-singular and write \( p^\text{ns}_{l} = \abs{\calDl_{\text{ns}}} \).

Define the data tensor for non-singular cones as
\( \leftindex_{\text{ns}}{X}^{(1)} = X \)
and
\[
    \leftindex_{\text{ns}}{\Xll} \odot \Tl = \sum_{j_l = 1}^{p^{\text{ns}}_l}
    \Dl_{j_l}\leftindex_{\text{ns}}{\Xl} \odot \Tl_{j_l},
\]
where it should be understood that \( \Dl_{j_l} \in \calDl_{\text{ns}} \)
for every \( j_l \in [p_l^{\text{ns}}] \).
Using only non-singular cones in the convex reformulation
(Problem~\ref{eq:convex-tensor-program}) induces a modified convex
decomposition constraint, which we refer to as \( \calCk_{\text{ns}} \).
Analyzing \( \calCk_{\text{ns}} \) reveals that including only non-singular
cones removes any limitations on \( \Tk \).

\begin{restatable}{lemma}{deepNonSingularCones}\label{lemma:deep-non-singular-cones}
    Consider restricting the tensor decomposition constraint
    \( \calCl \) to non-singular cones.
    That is, let \( \calC^{(1)}_{\text{ns}} = \R^{d_0 \times d_1} \)
    and
    \begin{equation}
        \begin{aligned}
            \calC^{(l+1)}_{\text{ns}}
             & = \bigg\{
            \Tll \in \R^{d_0 \times p^\text{ns}_1 \cdots \times p^\text{ns}_{l} \times d_{l+1}}
            :
            \Tll_{j_{l}, i_{l+1}}
            = \Tl_{ \phi_l(1, j_l, i_{l+1})}
            - \Tl_{ \phi_l(-1, j_l, i_{l+1})}, \\
             & \hspace{3em}
            \Tl_{\phi_l(1, j_l, i_{l+1})}, \Tl_{ \phi_l(-1, j_l, i_{l+1})}
            \in \calK^{(l)}_{j_{l}}, \text{ and }
            \Tl \in \calC_\text{ns}^{(l)}
            \bigg\},
        \end{aligned}
    \end{equation}
    where it should be understood that the indices
    \( j_l \in [p_l^\text{ns}] \) range only over non-singular cones.
    Then it holds that
    \( \calCll_{\text{ns}}
    = \R^{d_0 \times p^\text{ns}_1 \cdots \times p^\text{ns}_{l} \times d_{l+1}} \).
\end{restatable}

Since \( \Xl \odot \Tl \) is linear, it admits a representation
as matrix multiplication between an expanded data matrix \( \mathbf{X}^{(l)} \)
and a matrix version of the tensor \( \Tl \), which we call \( \mathbf{T}^{(l)} \).
As such, our results on cone containment from \cref{chapter:fast-optimization}
(\cref{thm:cone-elimination}) immediately extend to deep networks.

\begin{restatable}{proposition}{deepConeElimination}\label{prop:deep-cone-elimination}
    Non-singular cones do not contribute to the convex reformulation for
    deep ReLU networks.
    That is, the convex reformulation
    \begin{equation*}
        \min_{\Tk \in \calCk} \calL\rbr{\Xk \odot \Tk, y}.
    \end{equation*}
    is equivalent to the same problem where singular cones are omitted
    \begin{equation}\label{eq:non-singular-cone-problem}
        \min_{\Tk} \calL\rbr{\Xk \odot \Tk, y}.
    \end{equation}
\end{restatable}

As a corollary, we show that training deep ReLU networks is equivalent to
solving an unconstrained (convex) tensor program.

\begin{restatable}{theorem}{coneDecompFormulation}\label{thm:cone-decomp-formulation}
    If for every \( l \in [L-1]  \) it holds that
    \( d_l \geq m^{*}_{l} \) for some threshold \( m^{*}_{l} \leq c \, n^{L - l} \),
    then the deep ReLU network training problem
    \begin{equation*}
        \min_{\theta = (W^{(1)}, \ldots, \Wk)} \calL\rbr{f_{\theta}(X), y},
    \end{equation*}
    is equivalent to the unconstrained tensor program
    \begin{equation}
        \min_{\Tk}
        \calL\rbr{\Xk_{\text{ns}} \odot \Tk, y}.
    \end{equation}
\end{restatable}

\cref{thm:cone-decomp-formulation} is the culmination of this chapter.
It combines gated ReLU networks, cone decompositions, and deep convex
reformulations to show that training a \( L \)-layer ReLU network is equivalent
to an unconstrained optimization problem over tensors of order \( L+1 \).
Just as in the two-layer setting, the key ingredient is forming an expanded
data space (\( \Xk_{\text{ns}} \)) which omits singular activation patterns.

