%!TEX root=../../main.tex

\chapter{Conclusion}\label{chapter:conclusion}

This thesis studies neural networks from the perspective of convex
optimization.
Building on recent work by \citet{pilanci2020convexnn}, we develop and
analyze \emph{convex reformulations} of neural networks.
Convex reformulations re-write the non-convex training problem for neural
networks as a convex optimization program in a higher dimensional space.
We show that this enables both faster optimization
(\cref{chapter:fast-optimization}) and novel analysis of global optima
(\cref{chapter:solution-functions}) for two-layer ReLU networks.
We also show how to develop convex reformulations for ReLU neural networks
with arbitrarily many layers and extend a subset of our previous results
to this setting (\cref{chapter:deep-reformulations}).
However, we leave many open problems to future work.

In \cref{chapter:solution-functions}, we do not provide a definitive answer
to the set-valued continuity of the regularization path for two-layer ReLU
networks with weight-decay regularization.
While our analysis shows that the path cannot be continuous at \( \lambda = 0 \),
inner semi-continuity (openness) of the regularization path away
from \( 0 \) is not known.
This problem has significant impact on the computational complexity of
hyper-parameter tuning for two-layer ReLU networks and we hope to address
it in future work.

In \cref{chapter:deep-reformulations}, we do not establish the exact complexity
of solving our deep convex reformulations.
A rigorous characterization for the complexity relies on computing the number
of activation patterns achievable in the \( l^{\text{th}} \) layer of a ReLU
network.
Of particular interest is whether or not low-rank structure in the data
leads to a polynomial number of activation patterns as in the two-layer
setting.
Such a result would imply polynomial time optimization for any deep ReLU
network exceeding the width thresholds \( m^*_l \).

Another open question in the final chapter concerns whether or not our bounds
on the width thresholds are tight.
Although our requirement \( m^*_{l} \leq c \, n^{L - l} \) matches the
two-layer setting when specialized to \( L = 2 \),
it remains to prove lower bounds for \( L \geq 3 \).
We believe that developing precise characterizations for \( m_l^* \) is
necessary if the machine learning community is to fully understand the
complexity regimes for training neural networks.

Finally, extending our deep convex reformulations to handle regularized
problems is a critical research question that we are currently tackling.
Since two-layer ReLU networks are universal approximators, the key role of
depth is to provide a ``better'' function representation rather than a better
fit of the training data.
Better can mean several things: more parsimonious (using fewer neurons),
parameterizing a smoother function (lower norm in function space), or
simply generalizing better at test time.
Regularization is widely regarded as inducing these properties in neural
networks, so incorporating regularization is crucial to realizing the full
power of our convex reformulation framework.
