%!TEX root=../../main.tex

We study the structure and properties of solution sets for shallow
neural networks with (gated) ReLU activations.
Unlike previous work, we avoid non-convexity of neural networks
by studying the constrained group lasso,
a generalized linear model which unifies the convex reformulations of both
ReLU and gated ReLU networks.
We derive analytical expressions for the optima and all stationary
points of the training objective for two-layer ReLU networks.
Building on this characterization, we develop
conditions for the optimal neural network to be p-unique,
an algorithm for optimal pruning of neural networks,
and sensitivity results.
We demonstrate the utility of our framework
in experiments on MNIST, CIFAR-10, and the UCI datasets.

There is still much work to do in this area.
For example, we conjecture that the min-norm CGL solution,
which corresponds to the network minimizing a fourth-power penalty,
always has a continuous regularization path.
More generally, it remains to extend our characterization of the solution set to
deeper networks and vector-output models.


%We derive analytical expressions for the optimal set of the constrained
%group lasso, conditions for uniqueness of the solution,
%an algorithm for computing minimal solutions, and continuity/sensitivity results;
%by mapping back into the non-convex parameterization, we obtain comparable
%theorems characterizing two-layer neural networks.
%Highlights these results include an expression for every stationary point of a
%two-layer ReLU network and an effective algorithm for pruning neurons.



