%!TEX root = ../main.tex

\textbf{The Lasso and Group Lasso}:
Our work is most similar to \citet{hastie2007forward},
who consider homotopy methods, and
\citet{tibshirani2013unique}, who characterize the lasso solution set.
Limited results exist beyond the lasso.
\citet{tibshirani2011solution} analyze the generalized lasso,
while \citet{yuan2006model} show the group lasso is piece-wise linear
when \( X \) is orthogonal.
\citet{roth2008group} partially characterize the group lasso solution set,
while \citet{vaiter2012dof} derive stability results and degrees-of-freedom
for the group lasso.

\textbf{Neural Network Solution Sets}:
The most similar work is by \citet{cooper2021global}, who show that the
solution sets of over-parameterized ReLU networks with smooth activations are
low-dimensional manifolds.
This is consistent with our work, which establishes that two-layer networks
with non-smooth ReLU activations also have optimal sets living on
low-dimensional manifolds.
However, our proof is quite different;
we construct and analyze the optimal set, while \citet{cooper2021global}
provide only an existence result and do not characterize the structure of the
optimal manifold.

Another related area of research focuses on embedding principles.
The first work in this area is by \citet{fukumizu2000plateau}, who show
that stationary points of two-layer neural networks are preserved as the
hidden layer increases in width.
Follow-up work establishes similar embedding principles for adding single neurons
to deep neural networks \citep{zhang2021embedding} and for adding entire
layers \citep{bai2022depth}.
The results are largely unrelated to optimization, although
\citet{bai2022depth} argue that adding additional layers can convert local
minima to saddle-points, allowing for SGMs to escape and find global optima
\citep{lee2016escape}.

Other partial characterizations of solution sets are inspired by empirical
observations.
For example, mode connectivity --- the idea that global optimal are connected
by linear or non-linear paths in weight-space --- has been observed
experimentally by \citet{garipov2018mode, draxler2018barriers}.
Follow-up work \citet{nguyen2019connected, kuditipudi2019connectivity} give
conditions on the network architecture under which mode connectivity is
guaranteed to hold.
After publication of the work presented in this chapter, \citet{kim2024convex}
leveraged our description of the optimal set for a thorough description of how
mode connectivity evolves with network width.

\textbf{Sensitivity, Stability, and Pruning}:
See \citet{fiacco1990sensitivity} for a review of classical sensitivity results
from optimization theory;
similar to our work, these theorems are largely focused on computing gradients
of the optimal value function and optimal solution.
In the machine learning literature, gradients of this type have been explored
as part of differentiable optimization layers \citep{agrawal2019differentiable}
and hypergradient descent \citep{baydin2017online}.
We refer to \citet{bialock2020pruning} for an overview on pruning.
