%!TEX root=../../main.tex

\constraintReduced*
\begin{proof}
	Let \( w \) be as in the theorem statement.
	We starting by showing that \( w \) obtains the optimal objective value
	for the reduced problem:
	\begin{align*}
		\half \norm{\Xa \w_\act - y}_2^2 + \lambda \sum_{\bi \in \act} \norm{\wi}_2
		 & =
		\min_{w : \Ki \wi \leq 0} \,
		\half \norm{X w - y}_2^2 + \lambda \sum_{\bi \in \calB} \norm{\wi}_2                                   \\
		 & \leq
		\min_{\wa : \Ka \wa \leq 0} \, \half \norm{\Xa \wa - y}_2^2 + \lambda \sum_{\bi \in \act} \norm{\wi}_2 \\
		 & \leq \half \norm{\Xa \w_\act - y}_2^2 + \lambda \sum_{\bi \in \act} \norm{\wi}_2,
	\end{align*}
	where the last inequality makes explicit use of feasibility of \( \w_\act \).
	Since \( \w_\act \) is feasible for the reduced problem and attains the
	minimum objective value, it must be optimal.
	Note that it is straightforward to check that the active blocks of the min-norm
	dual parameter \( \rmin_\act \) are dual optimal for the reduced problem.

	Now, let \( \wa' \) be an optimal solution to the reduced problem.
	Since \( \rmin_\act \) is dual optimal for the reduced problem,
	\cref{prop:sol-fn-cgl} implies
	\[
		\wi' = \alpha_\bi' \vi,
	\]
	for every \( \bi \in \act \), with \( \alpha_\bi' \geq 0 \).
	Since \( \Xa \wa' = \Xa \wa \), we deduce
	\[
		\sum_{\bi \in \act} (\alpha_\bi - \alpha_\bi')\Xbi \bi = 0,
	\]
	which contradicts minimality of \( \w \) unless \( \alpha_\bi = \alpha_\bi' \).
	That is, \( \wa' = \wa \).
	We conclude that the reduced problem provides the unique minimal solution
	with support \( \act \).
\end{proof}

\begin{lemma}\label{lemma:second-order-stationary}
	Let \( w \in \solfn(\lambda) \) be minimal.
	Then \( w \) is a second-order stationary point of the reduced problem
	(\cref{eq:constraint-reduced}).
\end{lemma}
\begin{proof}
	Define \( M(w) \) to be the block-diagonal projection matrix given by
	\begin{equation}\label{eq:projection-matrix-block}
		M(w)_\bi
		= \frac{1}{\norm{\wi}_2} \rbr{I - \frac{\wi}{\norm{\wi}_2}\frac{\wi^\top}{\norm{\wi}_2}}.
	\end{equation}
	The Hessian of the Lagrangian of the reduced problem with respect to
	\( w \) is exactly
	\[
		\nabla^2_w \calL(\wa, \ra) =
		\Xa^\top \Xa + \lambda M_\act(w).
	\]
	A sufficient condition for \( w \) to be second-order stationary is
	that this Hessian is positive-definite.
	We now shows this fact holds.

	Clearly \( \nabla^2_w \calL(\wa, \ra) \) is positive semi-definite
	as it is the sum of a PSD projection matrix
	and a Gram matrix, which is always PSD.
	Let \( \bar w \in \R^{|\act|} \) such that \( \bar w \neq 0 \).
	Suppose that
	\begin{align*}
		0
		 & = \bar w^\top \nabla^2_w \calL(\wa, \ra) \bar w                    \\
		 & = \bar w^\top \Xa^\top \Xa \bar w + \bar w^\top\lambda M(w) \bar w \\
		 & = \norm{\Xa w}_2^2 + \lambda w^\top M(w) w.
	\end{align*}
	Since \( M(\bar w) \) is PSD,
	it must hold that
	\[
		\bar w^\top M(w) \bar w = 0,
	\]
	which is true if and only if \( \bwi = \beta_\bi \wi \),
	\( \beta_\bi \in \R \), for each \( \bi \in \act \).
	As a result, we find that
	\[
		\Xa w - \Xa \bar w = \sum_{\bi \in \act} (1 - \beta_\bi) \alpha_{\bi} \Xbi \vi = 0,
	\]
	which contradicts minimality of \( \bar w \) unless \( \beta_{\bi} = 1 \)
    for each \( \bi \in \act \).
	But then \( \norm{\Xa w}_2^2 > 0 \) and
	we conclude that the Hessian is positive-definite as desired.
\end{proof}

\localSolFn*
\begin{proof}
	Recall from \cref{prop:constraint-reduced} that \( \wa \) is the unique
	solution to the reduced group lasso problem.
	In fact, as we show in \cref{lemma:second-order-stationary}, \( \wa \) is
	a second order stationary point for the reduced problem.
	Now, combining this fact with LICQ and SCS
	and using standard results on differential sensitivity from optimization
	theory (see, e.g. \citet[Theorem 5.1]{fiacco1990sensitivity} and
	the references therein)
	we obtain the following:

	For \( (\lambda, y) \) in a neighborhood of \( \bar \lambda, \bar y \),
	there exists a unique once continuously differentiable function
	\[
		\tilde l(\lambda, y) =
		\begin{bmatrix}
			\tilde h(\lambda, y) \\
			\tilde g(\lambda, y),
		\end{bmatrix}
	\]
	such that \( \tilde h(\bar \lambda, \bar y) = \wa \),
	\( \tilde g(\bar \lambda, \bar y) = \rmin_\act \),
	and \( \tilde l(\lambda, y) \) is a primal-dual solution to the reduced
	problem.

	Now we show that \( \tilde l \) can be extended from the reduced problem
	to obtain a local solution function for the constrained group lasso.
	Define \( h(\lambda, y) \) such that
	\( h_\act(\lambda, y) = \tilde h(\lambda, y) \)
	and \( h_{\calB \setminus \act}(\lambda, y) = 0 \).
	We shall show how to extend \( g \) shortly.
	For \( \bi \in \act \), the pair
	\( h_{\bi}(\lambda, y), g_\bi(\lambda, y) \)
	verifies the KKT conditions (which are separable over block)
	since it verifies them for the reduced problem.
	So, we need only consider \( \bi \in \calB \setminus \act \).

	First, consider \( \bi \in \calB \setminus \equi \).
	In this case, we have
	\[
		\norm{\Xbi^\top (\bar y - X h(\bar \lambda, \bar y)) + \Ki \ri(\bar \lambda, \bar y)}_2
		< \bar \lambda,
	\]
	Since this inequality is strict and
	\[
		z(\bar\lambda, \bar y) = \Xbi^\top (\bar y - X h(\bar \lambda, \bar y)),
	\]
	is continuous in \( \bar \lambda, \bar y \),
	there exists a neighborhood of \( \bar \lambda, \bar y \)
	on which
	\[
		\norm{z(\lambda, y) + \Ki \ri(\bar \lambda, \bar y)}_2
		\leq \lambda.
	\]
	Since \( \ri(\bar \lambda, \bar y) \geq 0 \) and \( \wi = 0 \),
	dual feasibility and complementary slackness hold.
	We conclude that the extension
	\( g_\bi(\lambda, y) = \ri(\bar \lambda, \bar y) \)
	satisfies KKT conditions on this neighbourhood.

	Now suppose \( \bi \in \equi(\bar \lambda, \bar y) \setminus \act \).
	If
	\[
		\norm{\Xbi^\top (y - X h(\lambda, y))}_2 = \lambda,
	\]
	then taking \( g_\bi(y, \lambda) = 0 \) satisfies KKT conditions.
	Otherwise, observe that
	\[
		\norm{\Xbi^\top (\bar y - X h(\bar \lambda, \bar y)) + \Ki \ri(\bar \lambda, \bar y)}_2
		= \bar \lambda,
	\]
	must hold for some dual parameter \( \ri(\bar \lambda, \bar y) \)
	by KKT conditions.
	Moreover, SCS implies that we can choose the dual parameter to satisfy,
	\[ \ri(\bar \lambda, \bar y) > 0, \]
	since \( \Ki^\top \wi(\bar \lambda, \bar y) = 0 \).
	Finally, because
	\[ \Xbi^\top (y - X h(\lambda, y)) \]
	is a continuous function of \( (y, \lambda) \), taking
	\( \lambda, y \) sufficiently close to \( \bar \lambda, \bar y \)
	implies there exists \( \ri(\lambda, y) \geq 0 \) such that
	\[
		\norm{\Xbi^\top (y - X h(\lambda, y)) + \Ki \ri(\lambda, y)}_2
		\leq \lambda.
	\]
	Now we choose our extension to be
	\( g_\bi(\lambda, y) = \ri(\lambda, y) \)
	so that \( (h_\bi, g_\bi) \) satisfies stationarity of the Lagrangian
	as well.
	Since \( g_\bi \) is feasible and \( h_\bi \)  is the zero function,
	primal feasibility, dual feasibility, and complementary slackness also hold.

	Since \( l = (g, h) \) satisfies the KKT conditions in a local neighborhood
	of \( \bar \lambda, \bar y \), it is exactly a local solution function.
	Moreover, since \( g_{\calB \setminus \calA}(\lambda, y) = 0 \)
	over this neighborhood, it is easy to see that the gradient
	for parameter blocks in \( \calB \setminus \calA \)
	is \( 0 \).
	For \( g_\act \), \citet[Theorem 5.1]{fiacco1990sensitivity} implies that the
	gradients are given as follows:

	Recall from \cref{lemma:second-order-stationary},
	that \( M_\act \) is a block-diagonal projection matrix
	with blocks given by
	\[
		M(\bar w)_\bi = \frac{1}{\norm{\bwi}_2} \rbr{I - \frac{\bwi}{\norm{\bwi}_2}\frac{\bwi^\top}{\norm{\bwi}_2}}.
	\]
	Then, the Jacobian of \( \nabla_w \calL(\bar \wa, \bar \ra) \)
	for the reduced problem with respect to the primal-dual parameters is
	given by
	\[
		D =
		\begin{bmatrix}
			\Xa^\top \Xa + M(\bar w) & \Ka                            \\
			\bar \ra \odot \Ka       & \text{diag}(\Ka^\top \bar \wa)
		\end{bmatrix}.
	\]
	It also holds that \( D \) is invertible.
	Finally, let \( u_i = \frac{w_i}{\norm{\wi}_2} \)
	and \( u \) the concatenation of these vectors.
	We are now able to write the
	Jacobians of \( w(y, \lambda) \)
	with respect to \( y \) and \( \lambda \)
	as follows:
	\[
		\nabla_\lambda w(\bar \lambda, \bar y)
		= - [D^{-1}]_\act u_\act
		\quad \quad
		\nabla_y w(\bar \lambda, \bar y)
		= [D^{-1}]_\act \Xa^\top,
	\]
	where \( [D_\act^{-1}]_\act \) is the \( |\act| \times |\act| \)
	dimensional leading principle submatrix of \( D \).
\end{proof}

