%!TEX root=../main.tex

\prefacesection{Acknowledgements}

If raising a child takes a village, then completing a PhD takes at least a
small town.
Above all, I am greatly indebted to the advisors and mentors who supported my
research career from it's beginnings at the University of British Columbia
(UBC) to the submission of this thesis at Stanford.
At UBC, I would like to thank David Poole and Giuseppe Carenini for their
supervision during two NSERC USRAs.
Their support made my first experiences of research exciting and fulfilling.
At RIKEN AIP, I owe the most sincere thanks to Emtiyaz Khan, without whom I
would certainly not be working in optimization or machine learning today.
Mark Schmidt, my master's advisor at UBC, has been an unflagging supporter of
my career and I hope to benefit from his excellent advice for many more years
to come.
At Stanford, I am extremely grateful to have been supervised by Mert Pilanci,
whose patience with my peripatetic lifestyle went far beyond the call of duty.
I must also thank my many internship advisors: Robert Gower and Alberto Bietti at
the Flatiron Institute, Francis Bach at Inria Paris, and Sahand Negahban and
Deepak Rajan at the Voleon Group --- I could not have reached this point without
your help.
Finally, I have greatly appreciated the help and advice of my committee members,
Balaji Prabhakar, Aaron Sidford, Robert Tibshirani, and Stephen Boyd.

I would be remiss if I did not also mention the many contributions of my
friends and peers at different institutions.
I owe a great intellectual debt to Frederik Kunstner, but thankfully I think I
still have an edge on him when it comes to our ``insightful discussions''.
I must also single-out Si Yi (Cathy) Meng for our shared summer at the Flatiron
Institute, which was by-far the most fun period in my PhD, and Jonathan
Lavington for introducing me to climbing, without which I probably would have
many more grey hairs and one at least one more pulley.
At Stanford, I thank Burak Bartan, Daniel Cederberg, Tolga Ergen, Sungyoon Kim,
Arda Sahiner, and Emi Zeger for their myriad contributions.
Similarly, I want to acknowledge Eugène Berta and Sacha Braun at Inria, Yihan
(Joey) Zhou at UT Austin, and especially Sharan Vaswani at SFU.

Of course, the full list of people to whom I owe gratitude is longer than I can
enumerate here, so I will simply conclude by thanking my family and my partner
for their kindness through the ups and downs of the last five years.
