%!TEX root = ../main.tex

\section{Default Optimization Parameters}\label{app:default-parameters}

In this section, we report the standard parameter settings for our optimizers.
We use these parameters in all experiments unless explicitly stated otherwise.
Note that data normalization (Appendix~\ref{app:data-normalization}) is applied in all experiments for both the convex and non-convex training problems.

\subsection{R-FISTA}

We set the backtracking parameter to \( \beta = 0.8 \) and the forward-tracking parameter to \( \alpha = 1.25 \).
For the step-size initialization strategy, we set the threshold to be \( c = 5.0 \).
We set the first step-size to be \( \eta_0 = 1.0 \).
The restart strategy detailed in Section~\ref{sec:efficient-fista} is always used unless it is explicitly stated otherwise.
Finally, we consider the optimizer to have (approximately) converged when the minimum-norm subgradient has \( \ell_2 \)-norm less than or equal to \( 10^{-3} \).
In practice we check the equivalent condition on the squared gradient norm with the threshold \( 10^{-6} \).
We always initialize the model weights as \( v_i = 0 \) for each \( D_i \in \tilde \calD \).

\subsection{AL Method}

We set the initial penalty parameter to be \( \delta = 100 \) and use the windowing heuristic with \( r_u = 10^{-2} \) and \( r_l = 10^{-3} \).
The dual parameters are initialization at \( 0 \), as are the primal parameters.
Note that we always warm-start the optimization of the augmented Lagrangian at the solution to the previous iteration's optimization problem.
The convergence tolerance when checking for satisfaction of the windowing heuristic is set to be \( \text{tol} = 10^{-3/2} \).
If the constraint gap is larger than \( r_u \), we increase \( \delta \) as \( \delta \gets 2 * \delta \) and repeat the procedure.
If \( c_{\text{gap}} < r_l \), we set \( \delta \gets \delta / 2 \) and also change the convergence to be \( \text{tol} \gets \text{tol} / 2 \).

The convergence tolerance for minimization of the augmented Lagrangian once the window heuristic is satisfied is \( \text{tol} = 10^{-3} \).
We consider the AL method to have approximately converged when \( c_{\text{gap}} \leq 10^{-3} \) and the minimum norm subgradient of the augmented Lagrangian (with respect to the primal parameters) is also less than \( 10^{-3} \).

To solve Equation~\eqref{eq:al-subroutine}, we use R-FISTA with the standard configuration as outlined in the previous section.
We enforce a maximum of \( 1000 \) iterations for the sub-solver, meaning that we execute a step of the AL method after at most \( 1000 \) iterations of R-FISTA regardless of the termination tolerances.
In general, we permit as many ``outer'' iterations of the AL method as needed since these do not require gradient computations, but limit the overall optimization procedure to \( 10000 \) iterations of R-FISTA.
