%!TEX root=../main.tex

\chapter{Introduction}\label{chapter:introduction}

In 2012, AlexNet won the ImageNet Large Scale Visual Recognition Challenge
\citep{deng2009imagenet} and marked the ascendency of deep neural networks in
machine learning, a process which (arguably) began with Geoffrey Hinton's
famous MNIST digit generation demo in 2006 \citep{hinton2006deep}.
AlexNet won the competition with a top-five accuracy of \( 84.7\%  \) and at
the time was considered a ``large, deep convolutional neural network'' based on
its model size of sixty million parameters \citep{russakovksy2015imagenet}.
In comparison, the recent foundation model Florence
\citep{yuan2021florence} achieves top-five accuracy greater than \( 99\% \)
using 893 million parameters.
In addition to being much larger than AlexNet, Florence uses modern techniques
like contrastive learning, image transformers, and extensive pre-training on
800 million additional images.
The gaps between AlexNet and Florence in modeling, training data, and test
performance reflect the rapid advances machine learning has made since 2012.

While AlexNet took approximately seven days to train on two NVIDIA GTX 580 GPUs
\citep{krizhevksy2012alexnet}, Florence required 10 days to pre-train on 512
NVIDIA A100 GPUs.
This means Florence used roughly 365 times more GPU hours on machines with
between 12 (32 bit precision) and 48 (16 bit precision)
times more FLOPS and with 20 times more memory than those used for AlexNet.
Accounting for Florence's size and additional data implies a training
efficiency compared to AlexNet between \( 0.68 \) and \( 2.74 \)
\citep{a100, gpucomparison}.%
\footnote{Florence uses mixed-precision training, so an exact performance
    comparison is difficult.}
The point of these back-of-the-envelope calculations is to expose a dominant
trend in machine learning:
increasingly large models and data sets have led to remarkable improvements in
test performance, but training costs have increased proportionally and
training efficiency has stagnated.
In other words, advances in optimization for neural networks have not matched
the advances in neural networks themselves.

The key challenge in optimization for neural networks is non-convexity.
Unlike matrix factorization and other benign non-convex functions
\citep{burer2005low}, neural networks admit many saddle points and
local extrema.
As a result, global optimization for neural networks is NP-hard in general
\citep{froese2023hard, blum1988complete}.
Practitioners instead rely on stochastic gradient methods (SGMs) to find
stationary points. 
Despite the theoretical difficulty, highly accurate models are trained in practice using stochastic gradient methods (SGMs)~\citep{bengio2012practical}.
Unfortunately, SGMs cannot guarantee convergence to a local optimum of the non-convex training loss~\citep{ge2015escaping} and existing methods rarely certify convergence to a stationary point of any type~\citep{goodfellow2016deeplearning}.
SGMs are also sensitive to hyper-parameters;
they converge slowly, to different stationary points~\citep{neyshabur2017implicit}, or even diverge depending on the choice of step-size.
Parameters like the random seed complicate replications and can produce model churn, where networks learned using the same procedure give different predictions for the same inputs~\citep{henderson2018deep, bhojanapalli2021reproducibility}.
See \autoref{fig:synthetic-classification} for an example.
For most applications, practitioners use domain knowledge and costly hyper-parameter search to cope with these challenges.


Moreover, non-convexity prevents practitioners from using fast optimization
methods like Nesterov acceleration \citep{nesterov1983method}


\section{Preliminaries and Assumptions}

\section{Related Work}

\section{Published Papers and Multiple Authorship}
