%!TEX root=../../main.tex

Let \( X \in \R^{n \times d_1} \) be a matrix of observations and \( y \in
\R^{n \times c} \) a matrix of \( c \)-dimensional responses for each
observation.
This setup covers both multi-class classification and regression with
vector-valued targets.
We are interested in fully-connected ReLU neural networks with arbitrarily many
layers.
Let \( \Wl \in \R^{d_{l} \times d_{l+1}} \) be the matrix of weights for the \(
^{\text{th}} \) layer.
We will use \( \Wl_{i} \) to refer to the \( i^{\text{th}} \) row of \( \Wl \)
and \( \Wl_{\cdot, j} \) to refer to the \( j^{\text{th}} \) column.
The activations at layer $l$ are defined to be,
\begin{equation}
    Z^{(l+1)} = \rbr{\Z W^{(l)}}_+,
\end{equation}
where we take \( Z^{(1)} = X \) and \( \rbr{\cdot}_+ \) is ReLU activation
function defined element-wise as \( \rbr{z}_+ = \max\cbr{z, 0} \).
Using this notation, a fully-connected neural network with \( k \)-layers has
the prediction function given by,
\begin{equation}
    f_\theta(X) = Z^{(k)}
    W^{(k)},
\end{equation}
where \( W^{(k)} \in \R^{d_{k} \times c} \) ensures
that the prediction is of the right dimension.
Here, \( \theta = \cbr{W^{(1)}, \ldots, \Wk} \) denotes the collection of
weights for the network and \( \Theta \) the complete parameter space.
The choice of \( k = 2 \) corresponds to a two-layer ReLU network,
which is sometimes referred to as a network with one hidden layer.
In this case, the recursive definition can be unrolled to give a simple
and explicit prediction function,
\begin{equation}\label{eq:two-layer-vector-output}
    f_\theta(X) = \rbr{X W^{(1)}}_+ W^{(2)}.
\end{equation}
Many of our results are focused on two-layer ReLU networks with scalar
outputs, meaning \( c = 1 \).
In this setting, it will often be useful to break-down \( f_\theta \) into
an explicit sum over neurons in the hidden layer,
\begin{equation}\label{eq:two-layer-scalar-output}
    f_\theta(X) = \sum_{j = 1}^{d_2} \rbr{X W^{(1)}_{\cdot, j}}_+ W^{(2)}_{j}.
\end{equation}
Note that since \( c = 1 \), there is no weight sharing and \( W^{(2)} \in \R^{d_2 \times 1} \)
is a column vector.

We consider choosing \( \theta \) by solving a regularized empirical risk
minimization problem using the fixed training set \( (X, y) \).
That is, problems of the form,
\begin{equation}\label{eq:regularized-erm}
    \theta^* \in \argmin_{\theta \in \Theta}
    \calL\rbr{f_\theta(X), y} +
    \lambda R(\theta),
\end{equation}
where \( \calL \) is a strictly convex loss function, \( R \) is a (typically
convex) regularizer, and \( \lambda \geq 0 \) controls the strength of the
regularization.
The function
\begin{equation}
    F_\lambda(\theta) = \calL(f_\theta(X), y) + \lambda R(\theta)
\end{equation}
is referred to as the objective function.
Although \( \calL \) and \( R \) are usually convex, \( \theta \mapsto
F_\lambda(\theta) \) is not because the neural network \( f_\theta \) is
highly non-linear and itself non-convex.
As a result, Problem~\ref{eq:regularized-erm} is challenging to solve in both
theory and practice.

The most common choice of \( \calL \) and \( \R \) in practice are squared
error and \( \ell_2 \)-squared (weight-decay) regularization, respectively.
This leads to the following concrete optimization problem:
\begin{equation}\label{eq:squared-error}
    \theta^* \in \argmin_{\theta \in \Theta}
    \half \norm{f_\theta(X) - y}_2^2 +
    \frac{\lambda}{2} \sum_{l=1}^k \norm{\Wl}_F^2,
\end{equation}
where \( \norm{\cdot}_F \) is the Frobenius norm given by the sum of squared entries,
\[
    \norm{W}_F = \rbr{\sum_{i, j} W_{i, j}^2}^{1/2}.
\]
The squared-error loss function is equivalent to assuming a Gaussian likelihood
function and is a standard choice for regression problems.
Recent work has also shown that it performs comparably to cross-entropy for
classification problems \citep{hui2021evaluation}.
Similarly, \( \ell_2 \)-squared regularization is comparable to assuming
a Gaussian prior on the model weights;
from an optimization perspective, it is desirable because it gives curvature to
objective function, ensuring that \( F_\lambda \) is coercive and that the
level sets are compact.

We conclude by introducing background on convex reformulations.
In the following, we assume that \( \theta \) parameterizers a two-layer,
scalar output ReLU network as described in \cref{eq:two-layer-scalar-output}.
For such networks, convex reformulations re-write \cref{eq:regularized-erm} as
a convex program by enumerating the activations a single neuron in the
hidden layer can take on for fixed \( X \) as follows:
\[ \calD_Z = \cbr{D = \diag(\mathds{1}(X u \geq 0)) : u \in \R^d}. \]
This set grows as \(|\calD_Z| \le O(r(n/r)^r)\), where \(r := \text{rank}(X)\)
\citep{pilanci2020convexnn}.
Each ``activation pattern'' \( D_i \in \calD_{X} \) is associated with
a convex cone,
\[
    \calK_i = \cbr{u \in \R^d : (2D_i - I) X u \succeq 0}.
\]
If \( u \in \calK_i \), then \( u \) matches \( D_i \), meaning \( D_i X u = \rbr{X u}_+ \).
For any subset \( \tilde \calD \subseteq \calD_Z \),
the convex reformulation is,
\begin{equation}\label{eq:convex-relu-mlp}
    \begin{aligned}
        \min_{v, w} \, & L\Big(\sum_{D_i \in \tilde \calD} D_i X (v_i - u_i), y\Big)+\lambda\sum_{D_i \in \tilde \calD}\norm{v_i}_2+\norm{u_i}_2 \\
                       & \text{s.t.} \quad v_i, u_i \in \calK_i.
    \end{aligned}
\end{equation}
\citet{pilanci2020convexnn} prove that this program and \cref{eq:non-convex-relu-mlp}
are equivalent in the following sense:
if \( \tilde \calD = \calD_Z \) and \( m \geq m^* \) for some \( m^* \leq n + 1 \),
then the two programs have the same optimal value and every solution to the convex program
can be mapped to a solution of the non-convex training problem and vice-versa.
Given a solution \( \rbr{v^*, u^*} \), optimal weights
for the ReLU problem are given by
\begin{equation}\label{eq:convex-to-relu}
    \begin{aligned}
        W^{(1)}_{\cdot, i} & = v_i^*/ \sqrt{\norm{v_i^*}}, \quad W^{(2)}_{i} = \sqrt{\norm{v_i^*}}
        \\
        W_{1j}             & = u_i^*/ \sqrt{\norm{u_i^*}}, \quad w_{2j} = -\sqrt{\norm{u_i^*}},
    \end{aligned}
\end{equation}
where we use the convention that \( 0/0 = 0 \).

In practice, learning with \( \calD_{X} \) is intractable except when the data
are low rank.
In the following chapter, we provide refined conditions on \( \tilde \calD \)
which are sufficient for \cref{eq:convex-relu-mlp} to be equivalent to the
non-convex problem.

%Our analysis will work by considering the space of activation patterns that
%can be attained by a single ReLU neuron.
%Given a matrix \( A \in \R^{a \times b} \), set of activation patterns for \( A \) is
%\begin{equation}
%    \calD(X) = \cbr{ \text{diag}\rbr{\mathds{1}\rbr{ X w \geq 0}}: w \in \R^d }.
%\end{equation}
%Note that each pattern \( D_i \in \calD(X) \) is a diagonal matrix with \(
%[D_i]_{jj} = 1 \) if \( x_i^\top w \geq 0 \) and \( 0 \) otherwise.
%Each activation pattern is associated with a convex cone of vectors which
%are consistent with that pattern,
%\begin{equation}
%    \calK_i(X) = \cbr{w : (2D_i - I) X w \geq 0 }.
%\end{equation}
%It is straightforward to show that \( w \in \calK_i(X) \) if and only if \(
%(Xw)_+ = D_i X w \), i.e. \( D_i \) linearizes the ReLU activation.

%To reduce the burden of notation, let \( X^{(1)} = X \) and \( \calD^{(1)} =
%\calD(X) \).
%Let \( D^{(1)}_i \in \calD^{(1)} \) denote the activation patterns associated
%with \( X^{(1)} \) and \( \calK^{(1)}_i \) the associated cone.
%The total number of activation patterns is \( p_1 = \abs{\calD^{(1)}} \).
%Let \( a_1 = d_1 \) so that \( X^{(1)} \in \R^{n \times a_1} \).
%Then, we can recursively define,
%\begin{equation}
%    X^{(l+1)} =
%    \begin{bmatrix}
%        \Dl_1 \Xl & \ldots & \Dl_{p_{l}} \Xl
%    \end{bmatrix}
%    ,
%\end{equation}
%\( \calDl = \calD(\Xl) \), \( \Dl_i \in \calDl \) where \(
%\calKl_i \) is the associated cone, and \( p_l = \abs{\calD^l} \).
%Note that \( X^{(l+1)} \in \R^{n \times p_{l} \cdot a_{l}} \), which implies \(
%a_{l+1} = p_{l} \cdot a_{l} \).
%These objects will allow us to reason about the activation patterns of neural
%networks with more than two layers.
