%!TEX root = ../main.tex
\section{Convex Reformulations}\label{sec:convex-formulations}

Let \( X \in \R^{n \times d} \) be a data matrix and \( y \in \R^n \) the associated targets.
We are interested in two-layer ReLU networks,
\begin{equation*}
	h_{W_1, w_2}(X) = \sum_{i=1}^m \rbr{X W_{1i}}_+ w_{2i},
\end{equation*}
where \( W_1 \in \R^{m \times d} \), \( w_2 \in \R^m \) are the weights of the first and second layers, \( m \) is the number of hidden units, and \( \rbr{\cdot}_+ = \max\cbr{\cdot, 0} \) is the ReLU activation.
Fitting \( h_{W_1, w_2} \) by minimizing convex loss \( \calL \) with weight decay (\( \ell_2 \)) regularization leads to the optimization problem (NC-ReLU),\vspace{-1em}
\begin{equation}\label{convex-forms:eq:non-convex-relu-mlp}
	\min_{W_1, w_2} \! \calL\Big(h_{W_1, w_2}(X), y \Big) + \frac{\lambda}{2}\sum_{i=1}^m \norm{W_{1i}}_2^2 + |w_{2i}|^2,\!
\end{equation}
where \( \lambda \geq 0 \) is the regularization strength.
While Problem~\ref{convex-forms:eq:non-convex-relu-mlp} is non-convex,
\citet{pilanci2020convexnn} show that there is an equivalent convex optimization problem with the same optimal value if \( m \geq m^* \) for some \( m^* \leq n + 1 \). Furthermore, \citet{wang2021hidden} showed that all optimal solutions to \eqref{convex-forms:eq:non-convex-relu-mlp} can be found via the convex problem.

\subsection{Sub-Sampled ReLU Convex Programs}\label{sec:relu-models}

The convex reformulation for the NC-ReLU objective is based on ``enumerating'' the possible activations of a single neuron in the hidden layer.
The activation patterns a ReLU neuron \( \rbr{X w}_{+} \) can take for fixed \( X \) are described by
\[ \calD_X = \cbr{D = \diag(\mathds{1}(X u \geq 0)) : u \in \R^d}, \]
which grows as \(|\calD_X| \in O(r(n/r)^r)\) for \(r := \text{rank}(X)\) \citep{pilanci2020convexnn}.
For \( D_i \in \calD_{X} \), the set of vectors \( u \) which achieve the corresponding activation pattern, meaning \( D_i X u = \rbr{X u}_+ \), is the convex cone,
\[
	\calK_i = \cbr{u \in \R^d : (2D_i - I) X u \succeq 0}.
\]
For any subset \( \tilde \calD \subseteq \calD_X \), we define the sub-sampled convex optimization problem (C-ReLU):
\begin{equation}\label{convex-forms:eq:convex-relu-mlp}
	\begin{aligned}
		\!\!\! \min_{v, w} \, & \calL\Big(\!\!\sum_{D_i \in \tilde \calD}\!\! D_i X (v_i \!-\! w_i), y\Big)\!+\!\lambda\!\sum_{D_i \in \tilde \calD}\!\norm{v_i}_2\!+\!\norm{w_i}_2. \\
		                      & \text{s.t.} \quad v_i, w_i \in \calK_i
	\end{aligned}
\end{equation}

\citet{pilanci2020convexnn} prove NC-ReLU and C-ReLU are equivalent using linear semi-infinite duality theory~\citep{ goberna2002semi}.
However, this result requires \( m \geq m^* \) and the full enumeration of the activations of a neuron: \( \tilde \calD = \calD_X \).
In practice, learning with \( \calD_{X} \) is computationally infeasible except for special cases where the data are low rank.
By introducing sub-sampled models, we relax the dependencies on \( m^* \) and \( \calD_X \) to simple inclusions involving \( \tilde \calD \).

%% Moved lemma statement to appendix for space.

%First, we reduce to a group \( \ell_1 \) regularized mixed-integer program using positive homogeneity of the ReLU activation.

%\begin{restatable}{lemma}{miFormulation}\label{lemma:mi-reformulation}
%    The non-convex problem NC-ReLU (Problem \ref{convex-forms:eq:non-convex-relu-mlp}) is equivalent to the mixed-integer program,
%    \begin{equation}\label{convex-forms:eq:mi-reformulation}
%        \begin{aligned}
%            \min_{W_1, w_2} \; & \calL\Big(\sum_{i = 1}^m \rbr{X W_{1i}}_+ w_{2i}, y\Big) + \lambda \sum_{i = 1}^m \norm{W_{1i}}_2 \\
%                               & \text{\emph{s.t.}} \; w_2 \in \cbr{-1, 1}^m.
%        \end{aligned}
%    \end{equation}
%\end{restatable}

%See \cref{app:convex-forms} for a proof.
%\cref{lemma:mi-reformulation} suggests splitting on the values of \( w_{2i} \) and then enumerating the ReLU activations functions, which gives the following theorem.

\begin{restatable}{theorem}{convexDualityFree}\label{thm:duality-free}
	Suppose \( \rbr{W_1^*, w_2^*} \) and \( \rbr{v^*, w^*} \) are global minima of the NC-ReLU~\eqref{convex-forms:eq:mi-reformulation} and C-ReLU~\eqref{convex-forms:eq:convex-relu-mlp} problems, respectively.
	If the number of hidden units satisfies
	\[ m \geq b := \sum_{D_i \in \tilde \calD} \abs{\cbr{v^*_i : v^*_i \neq 0} \cup \cbr{w^*_i : w^*_i \neq 0} }, \]
	and the optimal activations are in the convex model,
	\[ \cbr{\text{\emph{diag}}\rbr{X W_{1i}^* \geq 0 : i \in [m]} } \subseteq \tilde \calD, \]
	then the two problems have same the optimal value.
\end{restatable}
See \cref{app:convex-forms} for proof.
The advantages of this theorem over existing results are (i) the simple and duality-free proof, and (ii) the dependence on \( \tilde \calD \), which we show in \cref{sec:experiments} can be much smaller than \( \calD_X \) while still performing comparably to NC-ReLU.
\cref{thm:duality-free} also reveals that \( m^* \) is determined by the number of active ``neurons'' at the optimal solution of the full C-ReLU problem with \( \tilde \calD = \calD_X \).

%\begin{align*}
%    \rbr{\hat W_1^*, \hat w_2^*} \!=\!\!\!\bigcup_{D_i \in \tilde \calD_i}\!\!\!\cbr{\rbr{v^*_i, 1} : v^*_i \neq 0} \cup \cbr{\rbr{w^*_i, -1} : w^*_i \neq 0}
%\end{align*}
%is a global minimizer of Problem~\ref{convex-forms:eq:mi-reformulation} and, defining,
%\[
%    T(j) = \cbr{ i \in [m] : \text{diag}\rbr{X W_{1i}^* > 0} = D_j },
%\]
%we construct a solution to Problem~\ref{convex-forms:eq:convex-relu-mlp} as,
%\begin{equation*}
%    \rbr{\hat v^*, \hat w^*} \!=\! \bigg\{\!\sum_{i \in T(j)}\!\!W_{1i}^* \mathds{1}(w_{2i}^*\!=\!1), \!\!\!\sum_{i \in T(j)}\!\!\! W_{1i}^* \mathds{1}(w_{2i}^*\!=\!-1) \bigg\}_{j = 1}^m
%\end{equation*}

%\begin{corollary}
%    Combining \cref{thm:duality-free} gives formal conditions for equivalence of C-ReLU and NC-ReLU with \( m \) neurons.
%\end{corollary}

%\begin{remark}\label{remark:active-neurons}
%    Taking \( \tilde \calD = \calD_X \) and applying \cref{thm:duality-free} yields
%    \[ m^* = \sum_{D_i \in \calD_X} \abs{\cbr{v^*_i : v^*_i \neq 0} \cup \cbr{w^*_i : w^*_i \neq 0} }. \]
%\end{remark}

\subsection{Unconstrained Relaxation: Gated ReLUs}

Solving C-ReLU using scalable first-order methods typically requires projecting on \( \calK_i \), which is an expensive quadratic program in the general case.
To circumvent this, we consider the following unconstrained relaxation (C-GReLU):
\begin{equation}\label{convex-forms:eq:unconstrained-relu-mlp}
	\min_{u} \; \calL\Big(\sum_{D_i \in \tilde \calD} D_i X u_i, y\Big)+ \lambda \sum_{D_i \in \tilde \calD} \norm{u_i}_2.
\end{equation}
At first look, this problem is a high-dimensional GLM with group-\( \ell_1 \) regularization.
In fact, C-GReLU is the convex re-formulation of another neural network optimization problem.
Let \( \calG \subset \R^d \) and consider the model,
\[
	h_{W_1, w_2}(X) = \sum_{g_i \in \calG} \phi_{g}(X, W_{1i}) w_{2i},
\]
where \( \phi_{g}(X, u) = \text{diag}(\mathds{1}(Xg \geq 0)) X u \) is a ``gated ReLU'' activation function with fixed gate vector \( g \) \citep{fiat2019decoupling}.
C-GReLU is equivalent to training this gated ReLU network.

\begin{restatable}{theorem}{unconstrainedEquivalence}\label{thm:unconstrained-equivalence}
	Let \( g_i \in R^d \) such that \(\text{diag}(X g_i \geq 0) = D_i \) and \( \tilde \calG = \cbr{g_i : D_i \in \tilde \calD} \).
	Then, C-GReLU is equivalent to the following gated ReLU problem (NC-GReLU):
	\begin{equation}\label{convex-forms:eq:gated-relu-mlp}
		\!\min_{W_1, w_2}\! \calL\Big(\!\!\sum_{g_i \in \tilde \calG }\!\!\phi_{g_i}(X, W_{1i})w_{2i}, y\Big)\!+\!\frac{\lambda}{2} \!\! \sum_{g_i \in \tilde \calG}\!\!\norm{W_{1i}}_2^2 + w_{2i}^2. \!\!
	\end{equation}
\end{restatable}
See \cref{app:convex-forms} for proof.
We can use \cref{thm:unconstrained-equivalence} to fit Gated ReLU networks by (much easier) unconstrained minimization.
However, as the next section shows, we can also leverage C-GReLU to approximate or exactly solve the original ReLU problem.
